### 2015-07-13 narrative/intro.tex
format consistency

\paragraph{Simulation Perspective}
\label{subsec:sim-perspective}
A simulation scientist should ideally be able to
obtain an estimate of how much time will be required to write data,
and how much storage space is available during the simulations lifetime.
Further, they would like Quality of Service (QoS) assurances, and that
issues such as varying bandwidth can be handled appropriately and 
automatically. For example, a set of user-specified rules would allow 
the system to make autonomic decisions at runtime
\S\ref{sec:managing-data-life} \S\ref{sec:qos}.
%
Our approach is based on giving users the ability to define the utility of
their data \S\ref{sec:data-description}. This includes the ability to assign
varying levels of importance to individual data objects in their entirety,
or to specific subsets and pieces. Key research challenges include: (1)
developing an expressive and easy to use a program interface, (2) formulating
a system model that can support autonomic decision, for example, for saving
data based on user-defined importance and utility of
data \S\ref{sec:managing-data-life}), and (3) defining the interface between
the system and the back-end storage for both single and multiple running
applications \S\ref{sec:qos}.

@@

\paragraph{Storage System Perspective}
\label{subsec:storage-perspective}
From the perspective of the storage system, it is necessary to manage a
single I/O request from a user in the context of all requests from all
users, and try to optimize the entire system accordingly. This entails
providing quality of service (\S\ref{sec:qos} to the user to minimize
resource contention, distribute the data across all of the tiers of storage
in a known consistent manner (\S\ref{sec:init-plac-data}), and automatically move data from one part of
the storage hierarchy to another (\S\ref{sec:migration}).

One of our research objectives is to understand how the
storage system can interact with the middleware   so
that the data with the highest utility is kept on the fastest layers of the
storage system for as long as specified. We need to maintain 
QoS and therefore, be able to provide fuzzy estimates of the time it will take to write/read data from
the different layers to inform any migration/eviction decisions, and it
is also critical that the storage system can manage (discover and retrieve) the data across all of the
layers automatically, without user intervention. 
Our approach here is that the storage system needs to define bounds of time estimates
(min time, max time), and as our system evolves, we want to allow plug-ins which can help
reduce the range of the bounds.
Overall, our goal is to enable predictable performance acorss the storage system, and we will develop mechanisms to enable this
\S\ref{sec:naming-discovery}.

>>>>

\paragraph{Simulation Perspective}
\label{subsec:sim-perspective}
A simulation scientist should ideally be able to
obtain an estimate of how much time will be required to write data,
and how much storage space is available during the simulations lifetime.
Further, they would like Quality of Service (QoS) assurances, and that
issues such as varying bandwidth can be handled appropriately and 
automatically. For example, a set of user-specified rules would allow 
the system to make autonomic decisions at runtime
(\S\ref{sec:managing-data-life}, \S\ref{sec:qos}).
%
Our approach is based on giving users the ability to define the utility of
their data (\S\ref{sec:data-description}). This includes the ability to assign
varying levels of importance to individual data objects in their entirety,
or to specific subsets and pieces. Key research challenges include: (1)
developing an expressive and easy to use a program interface, (2) formulating
a system model that can support autonomic decision, for example, for saving
data based on user-defined importance and utility of
data (\S\ref{sec:managing-data-life}), and (3) defining the interface between
the system and the back-end storage for both single and multiple running
applications (\S\ref{sec:qos}).

@@

\paragraph{Storage System Perspective}
\label{subsec:storage-perspective}
From the perspective of the storage system, it is necessary to manage a
single I/O request from a user in the context of all requests from all
users, and try to optimize the entire system accordingly. This entails
providing quality of service to the user to minimize
resource contention (\S\ref{sec:qos}), distribute the data across all of the tiers of storage
in a known consistent manner (\S\ref{sec:init-plac-data}), and automatically move data from one part of
the storage hierarchy to another (\S\ref{sec:migration}).

One of our research objectives is to understand how the
storage system can interact with the middleware   so
that the data with the highest utility is kept on the fastest layers of the
storage system for as long as specified. We need to maintain 
QoS and therefore, be able to provide fuzzy estimates of the time it will take to write/read data from
the different layers to inform any migration/eviction decisions, and it
is also critical that the storage system can manage (discover and retrieve) the data across all of the
layers automatically, without user intervention. 
Our approach here is that the storage system needs to define bounds of time estimates
(min time, max time), and as our system evolves, we want to allow plug-ins which can help
reduce the range of the bounds.
Overall, our goal is to enable predictable performance acorss the storage system, and we will develop mechanisms to enable this
(\S\ref{sec:naming-discovery}).
